Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
forgotten >>>>>>> origin/master
leaf's biography appears twice
Fix curly brace
Fix biblio
Commands that we had in ef8812
hyphen in title: relevance-based instead of relevance based

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features}

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} %\ja{What are the initials OE, ELF, etc. for? Do we need them?}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

\bibliographystyle{unsrt}
\bibliography{biblio}
\printbibliography

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing and musical informatics (ATIAM) from the University Pierre and Marie Curie and the IRCAM laboratory, Paris, France, in 2013. Since 2013, he is a Ph.D student at Irccyn, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
>>>>>>> origin/master
\end{IEEEbiography}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features}

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} %\ja{What are the initials OE, ELF, etc. for? Do we need them?}
}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

%\bibliographystyle{unsrt}
%\bibliography{biblio}
\printbibliography

@@
